Fig2

### 2020-02-21 analysis/figure-2.Rmd
new candidate genes

## candidate genes 
```{r writefiles}
candidategenes <- c("OXT", "AVP", "GNRH1",  "AR", "POMC", "AGRP",
                       "CRH", "AVPR1A", "AVPR1B", "AVPR2",
                       "CYP19A1", "DRD1", "DRD2", "PRL", "PRLR", "SOX9")

table1 <- allDEG %>%
  filter(gene %in% candidategenes) %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  select(sex, tissue, control_bldg, lay_inc.d3, inc.d3_inc.d9,
        inc.d9_inc.d17, hatch_n5)  %>%
  arrange( tissue, sex)
table1

>>>>

## candidate genes 
```{r writefiles}
geneids <- read_csv("../metadata/00_geneinfo.csv")

candidategenes <- c("OXT", "AVP", "GNRH1",  "AR", "POMC", "AGRP",
                       "CRH", "AVPR1A", "AVPR1B", "AVPR2",
                       "CYP19A1", "DRD1", "DRD2", "PRL", "PRLR", "SOX9", 
                    "ESR1","ESR2", "LBH", "CDK1", "BRCA1",
                    "PTEN", "CREBBP", "FOS", "JUN", "EGR1",
                     "BDNF", "GRM2",
                    "KCNJ5", "CISH", "PTGER3", "CEBPD", "ZBTB16")

table1 <- allDEG %>%
  filter(gene %in% candidategenes,
         comparison != "group_bldg") %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  select(sex, tissue, bldg_lay, lay_inc.d3, inc.d3_inc.d9,
        inc.d9_inc.d17,inc.d17_hatch, hatch_n5, n5_n9)  %>%
  arrange( tissue, sex)
table1
